---
title: "Assignment 2"
format:
  html:
    embed-resources: true
editor: visual
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo       = TRUE, 
                      fig.height = 3, 
                      fig.width  = 6,
                      fig.align  = "center")
ggplot2::theme_set(ggplot2::theme_bw())
```

## Instructions

Complete the following exercises **using only the tidyverse packages** (e.g., `dplyr`, `tidyr`, `ggplot2`, `readr`, `stringr`, `forcats`, `lubridate`, `purrr`, etc.)

**Important:** This assignment is intended to assess your proficiency with the **tidyverse**. Solutions that use **base R** or **packages outside the tidyverse** to solve the problems will **not receive credit** unless explicitly permitted in the question.

1.  Load the necessary **tidyverse** libraries.
2.  Answer each question in a separate R code chunk.
3.  Provide a detailed explanation of your approach for each solution.
4.  Render your R Markdown document to an HTML file.
5.  Submit the rendered HTML file to Canvas.

# Question:

-   Task 1: Read data using a relative path

``` r
Example:
college_data <- read_csv("../data/collegedata.csv")
```

```{r}
library(tidyverse)
college_data <- read_csv("~/Downloads/collegedata.csv")
glimpse(college_data)
```

-   In Task 1, I loaded the tidyverse library, containing the necessary packages inside of it to complete this assignment (dplyr, readr, purrr, ggplot2, etc.). Then, I loaded in the data, storing the data frame as `college_data`, and used `glimpse()` to get a quick look at the top of the data set.

-   Task 2:Determine rows and columns

    ```{r}
    nrow(college_data)
    ncol(college_data)
    ```

    In Task 2, I used the `nrow()` and `ncol()` functions to get the number of rows and columns in `college_data`. It returned 7175 rows and 12 columns in the console.

-   Task 3: Use tidyverse to select INSTNM, SAT_AVG, and ADM_RATE

    ```{r}
     selected_data <- college_data |>
      select(INSTNM, SAT_AVG, ADM_RATE)
    ```

    In Task 3, I created a new filtered data set, `selected_data`, which only looks at the University name, SAT average and ADM rate. I used the piping operator to select these variables and assigned them to a new data set.

-   Task 4: Create a scatterplot for SAT_AVG and ADM_RATE (Remove NA)

## Submission

-   After completing **each question**, save your Quarto file, render it, then **stage and commit** your changes.

-   Each commit should:

    -   Represent **one logical change**.
    -   Have a **short, descriptive** commit message.
    -   Be written in the **present tense** (imperative mood).

    **Examples:**

    **Bad:** `Fix bug in the project` *Too vague—it does not explain which bug was fixed.*

    **Bad:** `Fixed crash on login screen when password is empty` *Uses the past tense.*

    **Good:** `Fix crash on login screen when password is empty`

-   Include well-commented code and clear explanations for each solution.

-   Make **at least one meaningful commit per question/part** (a minimum of **4 meaningful commits**).

-   **Push your work to your** GitHub\*\*. ane post the link on the text bar of the Canvas assignment.

-   Assignments that are **not pushed to GitHub** will receive **no more than 60% of the available points**.

-   Submit the rendered HTML file to **Canvas**. Assignments that are **not submitted to Canvas** will also receive **no more than 60% of the available points**.

-   If you forget to submit your work to **GitHub** or **Canvas**, you have **up to three (3) days** after the due date to correct the submission. A **10% late penalty** will be applied to the assignment. **After three days, no submissions or corrections will be accepted.**

-   **No corrections, re-submissions, or missing submissions will be accepted after the assignment has been graded**, including forgotten GitHub or Canvas submissions.

**Good luck!**
